Output Summary

### 2020-11-20 03-post-process/output-plots.Rmd
Output plots: delete calculation of MCSE in diagnostics
This was causing some crashes with the error: result would be too long a vector. It is related to the mcmcse package somewhere. We are mostly concerned with Rhat and Neff anyways

# calculate the diagnostic statistics for each group
diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T, mcse = T)[c("mean", "Rhat", "neff", "mcse_mean"),])

# count up the number of parameters by group that fail to meet certain thresholds
diag_summ = t(sapply(diags, function(param) {
  mc_cv = (param["mcse_mean",]/param["mean",]) * 100
  c(
    n_total = ncol(param),
    n_Rhat_1 = sum(param["Rhat",] > 1.05),
    n_Rhat_2 = sum(param["Rhat",] > 1.1),
    n_Rhat_3 = sum(param["Rhat",] > 1.2),
    n_neff_1 = sum(param["neff",] < 2000),
    n_neff_2 = sum(param["neff",] < 1000),
    n_neff_3 = sum(param["neff",] < 500),
    mc_cv_1 = sum(mc_cv > 1),
    mc_cv_2 = sum(mc_cv > 5),
    mc_cv_3 = sum(mc_cv > 10)
  )
}))

# format to a table
diag_summ = as.data.frame(diag_summ)
colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500", ">1%", ">5%", ">10%")
df = cbind("Match" = unlist(lapply(diag_params, paste, collapse = ", ")), diag_summ)

# render the table
kable(df, align = "lcccccccccc") %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3, "MCMC SE/Mean * 100%" = 3)) %>%
  column_spec(1, monospace = T) %>%
  column_spec(c(2,5,8), border_right = T)

>>>>

# calculate the diagnostic statistics for each group
diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T)[c("mean", "Rhat", "neff"),])

# count up the number of parameters by group that fail to meet certain thresholds
diag_summ = t(sapply(diags, function(param) {
  c(
    n_total = ncol(param),
    n_Rhat_1 = sum(param["Rhat",] > 1.05),
    n_Rhat_2 = sum(param["Rhat",] > 1.1),
    n_Rhat_3 = sum(param["Rhat",] > 1.2),
    n_neff_1 = sum(param["neff",] < 2000),
    n_neff_2 = sum(param["neff",] < 1000),
    n_neff_3 = sum(param["neff",] < 500)
  )
}))

# format to a table
diag_summ = as.data.frame(diag_summ)
colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500")
df = cbind("Match" = unlist(lapply(diag_params, paste, collapse = ", ")), diag_summ)

# render the table
kable(df, align = "lccccccc") %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3)) %>%
  column_spec(1, monospace = T) %>%
  column_spec(c(2,5), border_right = T)
